Modelling at-bats in baseball using the generalised Pareto distribution

### 2024-01-25 bibat/examples/baseball/docs/report.qmd
Update baseball case study

```{.zsh}
> bibat
Welcome to the Batteries-Included Bayesian Analysis Template!
What is your project called? [Project Name]: Baseball
What should the project repository be called [baseball]: baseball
What is your name? [Author name]: Teddy Groves
What is your email? [author@email.com]:
Who should be the code of conduct contact? [author@email.com]:
Please briefly describe your project [A short description of the project.]: Comparison of distributions for modelling baseball hitting
Choose an open source license from these options: (MIT, BSD-3-Clause, No license file) [MIT]:
How would you like to document your project? (Quarto, Sphinx, No docs) [Quarto]:
Would you like to create a tests directory? [y]: n
Would you like to create a .github directory? [y]: n
>
```

@@

```{.zsh}
baseball
├── CODE_OF_CONDUCT.md
├── LICENSE
├── Makefile
├── README.md
├── bibat_version.txt
├── data
│   └── raw
│       ├── raw_measurements.csv
│       └── readme.md
├── docs
│   ├── bibliography.bib
│   ├── img
│   │   ├── example.png
│   │   └── readme.md
│   ├── report.html
│   ├── report.pdf
│   └── report.qmd
├── baseball
│   ├── __init__.py
│   ├── data_preparation.py
│   ├── fitting_mode.py
│   ├── inference_configuration.py
│   ├── investigate.ipynb
│   ├── notebooks
│   ├── prepare_data.py
│   ├── readme.md
│   ├── sample.py
│   ├── stan
│   │   ├── custom_functions.stan
│   │   ├── multilevel-linear-regression.stan
│   │   └── readme.md
│   ├── stan_input_functions.py
│   └── util.py
├── inferences
│   ├── fake_interaction
│   │   └── config.toml
│   ├── interaction
│   │   └── config.toml
│   └── no_interaction
│       └── config.toml
├── plots
│   ├── posterior_ll_comparison.png
│   └── posterior_predictive_comparison.png
└── pyproject.toml
```

@@

```zsh
> source .venv/bin/activate
(baseball) > python baseball/fetch_data.py
Fetching 2006 data from https://raw.githubusercontent.com/stan-dev/example-models/master/knitr/pool-binary-trials/baseball-hits-2006.csv
Writing 2006 data to data/raw/2006.csv
Fetching bdb-main data from https://raw.githubusercontent.com/chadwickbureau/baseballdatabank/master/core/Batting.csv
Writing bdb-main data to data/raw/bdb-main.csv
Fetching bdb-post data from https://raw.githubusercontent.com/chadwickbureau/baseballdatabank/master/core/BattingPost.csv
Writing bdb-post data to data/raw/bdb-post.csv
Fetching bdb-apps data from https://raw.githubusercontent.com/chadwickbureau/baseballdatabank/master/core/Appearances.csv
Writing bdb-apps data to data/raw/bdb-apps.csv
```

@@

```{.python include="../baseball/data_preparation.py" start-line=78 end-line=162}
```

@@

```{.python include="../baseball/data_preparation.py" start-line=36 end-line=56}
```

@@

```{.zsh}
> source .venv/bin/activate
(baseball) > python baseball/prepare_data.py
```

@@

But why stop there? It can also be useful to generate Stan input data with a
model, by running it in simulation mode with hardcoded parameter values. Here
are some functions that do this for both of our models:

```{.python include="../baseball/stan_input_functions.py" start-line=36}
```

>>>>

```{.zsh}
> bibat
Welcome to the Batteries-Included Bayesian Analysis Template!
What is your project called? [Project Name]: Baseball
What should the project repository be called [baseball]: baseball
What is your name? [Author name]: Teddy Groves
What is your email? [author@email.com]:
Who should be the code of conduct contact? [author@email.com]:
Please briefly describe your project [A short description of the project.]: Comparison of distributions for modelling baseball hitting
Choose an open source license from these options: (MIT, BSD-3-Clause, No license file) [MIT]:
How would you like to document your project? (Quarto, Sphinx, No docs) [Quarto]:
Would you like to create a .github directory? [y]: n
>
```

@@

```{.zsh}
baseball
├── CODE_OF_CONDUCT.md
├── LICENSE
├── Makefile
├── README.md
├── bibat_version.txt
├── data
│   └── raw
│       ├── raw_measurements.csv
│       └── readme.md
├── docs
│   ├── bibliography.bib
│   ├── img
│   │   ├── example.png
│   │   └── readme.md
│   ├── report.html
│   ├── report.pdf
│   └── report.qmd
├── baseball
│   ├── __init__.py
│   ├── data_preparation.py
│   ├── fitting_mode.py
│   ├── inference_configuration.py
│   ├── investigate.ipynb
│   ├── notebooks
│   ├── readme.md
│   ├── sample.py
│   ├── stan
│   │   ├── custom_functions.stan
│   │   ├── multilevel-linear-regression.stan
│   │   └── readme.md
│   ├── stan_input_functions.py
│   └── util.py
├── inferences
│   ├── fake_interaction
│   │   └── config.toml
│   ├── interaction
│   │   └── config.toml
│   └── no_interaction
│       └── config.toml
├── plots
│   ├── posterior_ll_comparison.png
│   └── posterior_predictive_comparison.png
├── pyproject.toml
└── tests
    ├── test_integration
    │   └── test_data_preparation.py
    └── test_unit
        ├── test_inference_configuration.py
        └── test_util.py
```

@@

```zsh
> source .venv/bin/activate
(baseball) > python baseball/fetch_data.py
Fetching 2006 data from https://raw.githubusercontent.com/stan-dev/example-models/master/knitr/pool-binary-trials/baseball-hits-2006.csv
Writing 2006 data to data/raw/2006.csv
Fetching bdb-main data from https://raw.githubusercontent.com/cbwinslow/baseballdatabank/master/core/Batting.csv
Writing bdb-main data to data/raw/bdb-main.csv
Fetching bdb-post data from https://raw.githubusercontent.com/cbwinslow/baseballdatabank/master/core/BattingPost.csv
Writing bdb-post data to data/raw/bdb-post.csv
Fetching bdb-apps data from https://raw.githubusercontent.com/cbwinslow/baseballdatabank/master/core/Appearances.csv
Writing bdb-apps data to data/raw/bdb-apps.csv
```

@@

```{.python include="../baseball/data_preparation.py" start-line=74 end-line=159}
```

@@

```{.python include="../baseball/data_preparation.py" start-line=25 end-line=32}
```

@@

```{.zsh}
> source .venv/bin/activate
(baseball) > python baseball/data_preparation.py
```

@@

But why stop there? It can also be useful to generate Stan input data with a
model, by running it in simulation mode with hardcoded parameter values. Here
are some functions that do this for both of our models:
^[These functions require some more imports: `numpy` and `scipy.special.expit`]
```{.python include="../baseball/stan_input_functions.py" start-line=36}
```
